### 2015-03-04 ThesisJo/background.tex
la2pdf commit - 2015:03:04	10:09:38	(Wed 4.Mar)
la2pdf commit - 2015:03:04	10:53:03	(Wed 4.Mar)
la2pdf commit - 2015:03:04	11:24:34	(Wed 4.Mar)

Light fast, sound slow.
Sound propagate far, light attenuated.

@@

\section{Coordinate System}

In this thesis we will relate all geometrical interpretations to the euclidean, spherical coordinate system shown in \Fig{geometry}. When assessing the imaging performance of a sonar its origin will be in the center of the array, but when assessing scenes its origin will be in the center of the image. A unit length vector $\vec u$ can be written as:
%
\begin{align*}
\vec u =
\begin{bmatrix}
\sin\theta \cos\phi \\
\sin\theta \sin\phi \\
\cos\theta
\end{bmatrix}
\end{align*}
%

@@

\section{Synethic Aperture Sonar Simulation}

>>>>

MVDR/LCA:
- Beamforming techniques.

Simulator:
- Scattering theory
- Coordinate systems

Common denominator:
- Image progressing
- High processing computing
- GPUs

Light fast, sound slow.
Sound propagates far, light attenuated.

@@

@@

\section{Array Processing}

Consider a monochromatic plane wave impinging on an $M$-element array (\Fig{geometry}). Let the position of sensor $m$ be $\p_m$, th  of sensors at locations 
In this thesis we will relate all geometrical interpretations to the euclidean, spherical coordinate system shown in \Fig{geometry}. When assessing the imaging performance of a sonar its origin will be in the center of the array, but when assessing scenes its origin will be in the center of the image. A unit length vector $\vec u$ can be written as:
%
\begin{align*}
\vec u =
\begin{bmatrix}
\sin\theta \cos\phi \\
\sin\theta \sin\phi \\
\cos\theta
\end{bmatrix}
\end{align*}
%

Signal model. Monochromatic, plane wave:
%
\begin{align}
\s[n] = \begin{bmatrix}
         s_0[n] \\ s_1[n] \\ \vdots \\ s_{M-1}[n]
        \end{bmatrix}
      = \begin{bmatrix}
         Ae^{j(\Omega n - \k\T\p_0)} \\
         Ae^{j(\Omega n - \k\T\p_1)} \\
         \vdots \\
         Ae^{j(\Omega n - \k\T\p_{M-1})}
        \end{bmatrix}
      = Ae^{j\Omega n}\a(\k)
\end{align}
%
where we call $\a(\k)$ the signal's \emph{steering vector}.

\section{Synethic Aperture Sonar}
